Response to Reviewers

### 2025-07-07 paper/review1/ReponseToReviewers2025.qmd
part way through revising paper

Add letter format

Add introductory thank you to reviewers for their work, and the editor for their consideration.

## To Do

Make a release version on github of current copy before changes

all points made be reviewers, must be addressed with a response using different font types for review comment v our response

In our Rmd file use XXX for difficult change to make - allocated to Di or Steph

# Review of “Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map  for Communicating Cancer Statistics”

Associate Editor

Dear associate editor XXX,

Thank you for the opportunity to improve this paper with the suggestions made in the comments provided. Please find our responses to the comments provided in *italics* below each paragraph or comment.

@@

Please see attached review.

@@

P8, L31-32. I would consider adding to the last sentence to write the following: “The  results are summarized in Section 4, followed by a discussion about the broader  implications for the use of this map style.

P9, L52. I’m on sure if the text in italics appears in the literature or if this is the author’s  view. If the author’s view then I would replace “doesn’t” with “does not”. If it appears in  the literature, please reference.

P9, L55. I would suggest replacing “better” with “adequately”.

P9, L77-78. Consider the following: “Figure 1 shows the hexagon tile map, where the  map is coloured from …

*Completed*

P10, L97. Omit the words “To do”.

*Completed*

*Completed*

P15, L226. Replace “will be” with “were”.

*Completed*

P15, L239-240. This could be written better. Should read a “logit” link. I would consider  writing the model as follows:

P16, L247. What is a “Figure Eight contributor ID”? : *This was used by the respondent to uniquely identify themselves and allow us to link them to the paid account we used for recruitment and payment. This reference has been removed, and in other places has been replaced with a unique identifier created for each participant.*

P11, Section 3.7. Could this information be captured more succinctly in a table  perhaps? Line 290-293 just lists words. There are no questions relating to these 3  dotpoints. I’m also wondering why participants do not submit their responses as they  go? Do they also have a chance to go back and change a response? It is difficult to  determine what this process is.

>>>>

Thank you for the careful reviews of our paper. Please find *our responses to provided in italics* point-by-point with the comments.

@@

XXX

P8, L31-32. I would consider adding to the last sentence to write the following: "The results are summarized in Section 4, followed by a discussion about the broader implications for the use of this map style."

*Done*

P9, L52. I'm on sure if the text in italics appears in the literature or if this is the author's view. If the author's view then I would replace "doesn't" with "does not". If it appears in the literature, please reference.

*Attributed to sentiment suggested by Monmonier (2018) How to Lie with Maps*

P9, L55. I would suggest replacing "better" with "adequately".

*Done*

P9, L77-78. Consider the following: "Figure 1 shows the hexagon tile map, where the map is coloured from …"

*Done*

P10, L97. Omit the words "To do".

*Done*

*We've reduced this part to a single sentence. The exact smoothing procedures for processing the null data sets can be found in the code on the GitHub repo. It is not important enough to report in detail. The `gstat` function produced null sets with insufficient spatial dependence, despite substantial adjusting parameters,  and so further simple smoothing was done. These were compared with the Atlas plots, which had very complicated procedures to produce the cancer maps, that also ensured privacy of information.*

*Several sentences have been added explaining why these three trend models was used.*

*Explained. It is because locations were randomly sampled.*

*Paragraph revised*

P15, L226. Replace "will be" with "were".

*Sentence removed because software is cited in the Acknowledgements.*

*Done*

P15, L239-240. This could be written better. Should read a "logit" link. I would consider writing the model as follows:

*Done*

P16, L247. What is a "Figure Eight contributor ID"?:

*This was used by the respondent to uniquely identify themselves and allow us to link them to the paid account we used for recruitment and payment. This reference has been replaced with a unique identifier created for each participant.*

P11, Section 3.7. Could this information be captured more succinctly in a table perhaps? Line 290-293 just lists words. There are no questions relating to these 3 dotpoints. I'm also wondering why participants do not submit their responses as they go? Do they also have a chance to go back and change a response? It is difficult to determine what this process is.

*Re-written. Responses were recorded on each lineup evaluation, but not saved in the Google sheet until the participant clicked Submit.*

@@
